---
name: Pedro N. de Lima
position: "Ph.D. Candidate, Pardee RAND Graduate School"
address: "1776 Main Street, Santa Monica, CA 90401-3208"
phone: +55 51 99214-0761
www: www.pedronl.com
#email: "pedronl@rand.org"
#twitter: pedroliman
#github: pedroliman
#linkedin: pedro-nascimento-de-lima
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
data_path = "C:/dev/cv/data.xlsx"
```

# Professional Summary

I am a Policy Research Assistant at RAND Corporation and a Ph.D. Candidate at Pardee RAND Graduate School (PRGS). My academic interests often gravitate towards the intersection between OR, Programming, and Management of Wicked Problems. My undergraduate and master’s dissertations focused on wicked problems and decision under deep uncertainty, have received the Best Brazilian Dissertation in Production Engineering Prize from ABEPRO, in 2016 and 2018, respectively.

# Work Experience

```{r}
#readxl::read_xlsx(data_path, "work-experience") %>%
#  detailed_entries(what = Title, when = Year, with = Company, why = Description)
```


# Awards

```{r}
#readxl::read_xlsx(data_path, "awards") %>%
#  detailed_entries(what = Title, when = Year, with = Source, why = Description)
```


# Publications

```{r publications}
#bibliography_entries("C:/dev/cv/publications.bib", "Publications")
```