---
name: Pedro N. de Lima
position: "Ph.D. Candidate"
address: "School of Physics & Chemistry, École Normale Supérieure"
phone: +1 22 3333 4444
www: www.pedronl.com
#email: "pedronl@rand.org"
#twitter: pedroliman
#github: pedroliman
#linkedin: pedro-nascimento-de-lima
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
data_path = "C:/dev/cv/data.xlsx"
```

# Professional Summary

I am a Policy Research Assistant at RAND Corporation and a Ph.D. Candidate at Pardee RAND Graduate School (PRGS). As an Engineer by training, I enjoy working at the intersection between Wicked Problems, Programming and Operations Research. For this reason, I branched out of Industrial Engineering and joined the RAND Corporation and PRGS aiming to further specialize in Policy Areas demanding advanced decision analytic approaches. 


# Awards

```{r}
readxl::read_xlsx(data_path, "awards") %>%
  detailed_entries(what = Title, when = Year, with = Source, why = Description)
```


# Publications

```{r publications}
bibliography_entries("C:/dev/cv/publications.bib", "Publications")
```